\section{Discussion and Limitations}

Three diagnostics were applied to a system whose aggregate score,
MAcc \num{0.866}, sits comfortably within the published range for this corpus.
All three point the same way. Unsupervised clustering recovers the acquisition
site far better than the diagnosis in two of three feature spaces. Per-site
performance ranges from \num{0.986} to \num{0.477}, with the pooled figure
carried by the single largest and easiest sub-database. And the model's
attribution, while genuinely dependent on learned weights and mildly
systole-preferring, is no more systole-preferring on correct decisions than on
incorrect ones.

None of these establishes a mechanism individually. Together they make it
difficult to maintain that a MAcc near \num{0.87} on this split demonstrates
learned cardiac acoustics, and easy to maintain that acquisition condition is
doing substantial work. We state that as an inference, and we name the
experiment that would settle it: training a classifier to predict the
sub-database from the same features, and measuring how much of the label
information survives after site is controlled for. We did not run it.

Several further limitations should be stated plainly rather than waited for.
The evaluation rests on one split of one corpus; recording-level splitting and
joint stratification protect against the most common leakage, but a single split
cannot separate representation effects from split-specific variance, and
repeated splits or nested cross-validation would give a firmer footing. Both
random forests overfit their training folds, and neither classical model is well
calibrated. The MFCC-to-frequency projection used in
Section~\ref{sec:xai} is sign-agnostic and approximate, and it disagrees with
the exact PWP mapping. Grad-CAM and Grad-CAM++ agree at only \num{0.392}, so
the temporal result is specific to one attribution variant. The segmenter
labels only \SI{66.5}{\percent} of test windows with sufficient confidence, and
nothing is known about whether the excluded third differs systematically ---
if low-confidence windows are the noisy ones, they may also be the ones where
site cues matter most. Finally, the two smallest sub-databases contribute
8 and 17 test recordings, and their figures carry essentially no statistical
weight.

We also note what did work. All five models substantially exceed trivial
baselines, and the ranking of feature domains is stable and interpretable: MFCC
outperforms PWP under both classifier families, and the log-Mel CNN attains the
best ranking quality (AUC \num{0.961}) despite an operating point that gives it
no MAcc advantage. The comparison the study was designed to make is therefore
answered, even though the answer is not the one anticipated.
